PDBF Documentation

### 2015-05-12 Documentation.tex
!

@@

\section{Chart options}
Macros: \\[3pt]
\verb|\chart[options][queryForOverlay]{queryForPage}| \\[8pt]
\noindent Options: \\[3pt]
\begin{tabular}{ll}
\textbf{chartType} & \\
Desc.:	&	Sets the type of the chart. \\
Argument:	&\verb|line or bar or signatureplot| (more info here)  \\
Default:&	\verb|line| \\[4pt]

@@

\textbf{quality} \\
Desc.:	&	Sets the quality for the image version of the chart. \\
& Can also be redefined globally (\verb|\pdbfQuality|). \\
Argument:	&Number $>$ 0 \\
Default:&	\verb|1.0| \\[4pt]

\textbf{scale} \\
Desc.:	&	Sets the scale for the chart. 1.0 corresponds roughly to 12pt in \LaTeX. \\
& Can also be redefined globally (\verb|\pdbfScale|). \\
Argument:	&Number $>$ 0 \\
Default:&	\verb|1.0| \\[4pt]

@@

\newpage
\section{F.A.Q.}
\begin{itemize}
\item Q.: The overlay is not on the right position \\
A.: Most likely you use pages with different sizes in your document. This is currently not supported by PBDF 
\item Q.: I get \verb|Error: paperwidth value missing! Did you forgot to specify the| \\ \verb|papersize via the geometry package?| when compiling my document \\
A.: You need to explicitly specify the papersize of your document via the geometry package (e.g. \verb|\usepackage[letterpaper]{geometry}|)
\end{itemize}

>>>>

%problems with utf8 package. for german umlauts use ngerman package instead. 
%if you really have to use the utf8 package then you cant use special characters inside queries.

@@

\section{Chart options}
Macros: \\[3pt]
\verb|\chart[options][queryForOverlay]{queryForPage}| \\
Note: if \verb|queryForOverlay| is omitted the \verb|QueryForPage| is used for the overlay\\[8pt]
\noindent Options: \\[3pt]
\begin{tabular}{ll}
\textbf{chartType} & \\
Desc.:	&	Sets the type of the chart. \\
Argument:	&\verb|line or bar or signatureplot| (more info here)  \\
Default:&	\verb|line| \\[4pt]

@@

%TODO: not yet implemented
%\textbf{overlap} \\
%Desc.:	&	unused \\
%Argument:&	\verb|-| \\
%Default:&	\verb|-| \\[4pt]

legendpos

includeZero

drawPoints

fillGraph

showRangeSelector

\textbf{quality} \\
Desc.:	&	Sets the quality for the image version of the chart in the pdf. 1.0 corresponds roughly to 120 pixels per inch \\
& Can also be redefined globally (\verb|\pdbfQuality|). \\
Argument:	&Number $>$ 0 \\
Default:&	\verb|1.0| \\[4pt]

\textbf{scale} \\
Desc.:	&	Scales the size of the chart. 1.0 corresponds roughly to font-size that is currently choosen in \LaTeX. \\
& Can also be redefined globally (\verb|\pdbfScale|). \\
Argument:	&Number $>$ 0 \\
Default:&	\verb|1.0| \\[4pt]

@@

%TODO: Pivot
%TODO: MultiplotChart

%\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"aggregation": "\pdbf@aggregation",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"aggregationattribute": "\pdbf@aggregationattribute",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"aggregationBig": "\pdbf@aggregationBig",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"aggregationattributeBig": "\pdbf@aggregationattributeBig",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"xCount": \pdbf@xCount,}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"yCount": \pdbf@yCount,}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"leftArr": "\pdbf@leftArr",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"rightArr": "\pdbf@rightArr",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"topArr": "\pdbf@topArr",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"bottomArr": "\pdbf@bottomArr",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"xValues": "\pdbf@xValues",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"yValues": "\pdbf@yValues",}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"yFirst": \pdbf@yFirst,}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"forceXequal": \pdbf@forceXequal,}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"forceYequal": \pdbf@forceYequal,}% 
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"cols": "\pdbf@cols",}%
%		\immediate\write\tempfile{\space\space\space\space\space\space\space\space\space\space\space\space"rows": "\pdbf@rows",}%

%TODO: \sql[textForPage]{queryForOverlay}
%TODO: \dbSQLText{sqlQueryString}
%TODO: \dbSQLFile{fileWithSqlQueries}
%TODO: \dbSQLJDBC{jdbcConnectionURL}{user}{password}{commaSeperatedListOfTableNames}
%jdbcConnectionURL consist of ... (e.g. jdbc:postgresql://localhost:5432/postgres)
%Note: jdbcConnectionURL, user, and password are not stored in the output document

\newpage
\section{F.A.Q.}
\begin{itemize}
\item Q.: The overlay is not on the right position \\
A.: Most likely you use pages with different sizes in your document. This is currently not supported by PBDF 
\item Q.: I get \verb|Error: paperwidth value missing! Did you forgot to specify the| \\ \verb|papersize via the geometry package?| when compiling my document \\
A.: You need to explicitly specify the papersize of your document via the geometry package (e.g. \verb|\usepackage[letterpaper]{geometry}|)
%TODO: check utf8 error message and put a faq entry here
\end{itemize}
